Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: version 1

\documentclass{article}

\usepackage{cite}
\usepackage[utf8]{inputenc}
\usepackage{hyperref,amsmath,amssymb,amscd}
\usepackage{amsthm}
\usepackage{color}
\usepackage{bbm}
\usepackage{appendix} 
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\newtheorem{remark}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{notation}{Notation}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{conjecture}{Conjecture}[section]

\title{Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
\author{Jianjie Zhao }

\begin{document}
%%给公式前加章节编号
\makeatletter
\@addtoreset{equation}{section}
\makeatother
\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}

@@

\section{Introduction}
\subsection{Model}

We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm. Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$. For any $f \in C^2(\mathbb{R}^d)$,
\begin{equation}\label{generatior}
Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
\end{equation}
where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.

For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.

In this paper, we consider a branching mechanism of the form  
\begin{equation}\label{mechanism}
\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
\end{equation}
Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.

Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have 
\begin{equation} \label{super}
    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
\end{equation}
where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
\end{equation}
According to \cite[section 2]{ZL}, is equivalent to
\begin{equation}\label{eq2}
     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
\end{equation}

In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$. We assume that the parameter $\alpha$ in branching mechanism $\psi$ is larger than zero, i.e. $X$ is  supercritical.

 The existence of such superprocesses is well known, see \cite{EB} for instance. Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{AK}. Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have
$$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$

For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup} 
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x) := \Pi_x [e^{\alpha t}f(\xi_t)], \quad x\in \mathbb{R}^d,t\geq 0,
\end{equation}
which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
\begin{equation}\label{meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle] = \langle T_t^{\alpha t}f, \mu \rangle.
\end{equation}
see \cite[Proposition 2.27]{ZL}.  Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.

The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.

\subsection{OU semigroup and Eigenfunctions}

Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
\begin{equation}\label{invariantdensity}
    \varphi (x) =\left (\frac{b}{\pi \sigma^2}\right )^{\frac{d}{2}}\exp \left(-\frac{b}{\sigma^2}|x|^2 \right ),\quad x\in \mathbb{R}^d.
\end{equation}
Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
$$\langle f_1, f_2 \rangle_{\varphi} = \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).$$

For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ... \cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ... \cdot \partial x_d^{p_d}$. We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$

$$H_p(x):=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).$$
It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)= \frac{1}{\sqrt{p!2^{|p|}}}H_p \left(\frac{\sqrt{b}}{\sigma}x \right ),\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
\end{equation}
 The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)=e^{-b|p|t}\phi_p(x),\quad x\in \mathbb{R}^d.
\end{equation}
Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
\begin{align}
    f=\sum_{k=0}^{\infty}\sum_{|p|=k}a_p \varphi_p \quad {\rm in~} L^2(\varphi), \label{semicomp1}
\end{align}
where $a_p=\langle f, \phi_p \rangle_{\varphi}$. Let
\begin{equation}\label{order}
    \kappa(f):=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
\end{equation}
denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.

In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
\begin{align*}
     \mathcal{P}:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}
\end{align*}

It is easy to see that $\mathcal{P} \subset L^2(\phi)$. What's more, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$
\begin{equation}\label{semigroupineq}
    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x) 
\end{equation}

That is to say the rate of decay of the semigroup depending on $\kappa(f)$. The readers can find the prove in \cite[Fact 1.2]{MM}.

@@

Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{ZL} to \eqref{charequation}, we have that
\begin{equation}\label{chareq2}
        w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x)
\end{equation}

@@

For each $p\in \mathbb{Z}_+^d$, we define 
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
 We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{theorem}\label{Theorem11}
     If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa(g)b)t}\langle g, X_t\rangle \rightarrow\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0\leq\gamma<\beta$.

     Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{theorem}
For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.  
 \begin{remark}
    If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle g, X_t\rangle \rightarrow \langle g, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0\leq\gamma<\beta$.

    Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{remark}

\subsubsection{Critical Branching Rate}
For $g\in \mathcal{P}$, define 
$$\tilde{m}[g]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
{\color{red}where} 
$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g,\phi_p\rangle\phi_p(x).$$
See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
\begin{theorem}\label{Theorem12}
Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle g,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by 
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
\end{theorem}

@@

\begin{lemma}\label{lemma24}
For any $0\leq \gamma < \beta$ there exists a constant $C>0$, we have the result:

@@

>>>>

%%%----Versions-----------------------------
% supCLT1.tex 2018/6/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{color}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
%---Top matter------------------------------
\begin{document}
\title
    %{\large Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching}
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Zhenyao Sun and Jianjie Zhao}
%---Yan-Xia Ren
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%---Zhenyao Sun
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
%---Jianjie Zhao
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{???@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}

@@

%---Contents-----------------------
\section{Introduction}
\subsection{Model}
%We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm. Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$. For any $f \in C^2(\mathbb{R}^d)$,
%\begin{equation}\label{generatior}
%Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
%\end{equation}
%where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.
Let $d \in \mathbb N:= \{1,2,\dots\}$.
For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm. 
Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
\begin{equation}\label{generatior}
    Lf(x)
    %= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x)), 
    = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x), 
    \quad f \in C^2(\mathbb{R}^d), 
\end{equation}
where $\sigma>0$ and $b>0$. 
%For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.
Denoted by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
%In this paper, we consider a branching mechanism of the form  
%\begin{equation}\label{mechanism}
%\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
%\end{equation}
%Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.
Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta}, 
    \quad z \in \mathbb C_+,
\end{equation}
where $\alpha > 0$ and $\beta \in (0,1) $.
%Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. 
Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of finite measures on $\mathbb{R}^d$.
%We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have 
%\begin{equation} \label{super}
%    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
%\end{equation}
%where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
%\begin{equation}\label{eq1}
%     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
%\end{equation}
%In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$. We assume that the parameter $\alpha$ in branching mechanism $\psi$ is larger than zero, i.e. $X$ is  supercritical.
In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$.
We say a $\mathcal{M}(\mathbb{R}^d)$-value Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle u_f(\cdot , t), \mu \rangle}, 
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
where $(x,t) \mapsto u_f(x, t)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
     u_f(x , t) + \Pi_x \Big[ \int_0^t\psi\big(u_f(\xi_s,t-s)\big)~ds\Big] 
     = \Pi_x [f(\xi_t)],
     \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

%According to \cite[section 2]{Li2011Measure}, is equivalent to
According to \cite[section 2]{Li2011Measure}, the above is equivalent to
\begin{equation}\label{eq2}
     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
\end{equation}

    The existence of such superprocesses is well known, see \cite{EB} for instance. 
    %Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. 
    %The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{Kyprianou2014Fluctuations}. 
    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example. 
    %Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have $$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$
    In fact, 
\begin{equation}
    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.

%For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup}
    Define the \emph{Fenyman-Kac semigroup} by  
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x) 
    := \Pi_x [e^{\alpha t}f(\xi_t)],
    %\quad x\in \mathbb{R}^d,t\geq 0, 
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
%which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle] 
    = \langle T_t^\alpha f, \mu \rangle,
%new
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
%end new
\end{equation}
%see \cite[Proposition 2.27]{Li2011Measure}. 
%Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.
Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.

%The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
%$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
%we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.

%\subsection{OU semigroup and Eigenfunctions}
\subsection{OU semigroup}
({\bf Do we have a good reference about those following result about the OU semigroup?})
Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
\begin{equation}\label{invariantdensity}
    \varphi (x) 
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
\end{equation}
Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
\langle f_1, f_2 \rangle_{\varphi} 
%= 
:=
\int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}

    %For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ... \cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ... \cdot \partial x_d^{p_d}$. We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$
    For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$. 
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    %:=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
%It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
%$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
It is known that, see \cite{GD} for example, the generator $L$ of OU process $\xi$ can be viewed as an operator 
%on $L^2(\phi)$ 
on $L^2(\varphi)$ 
with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
\begin{equation}
    A_k 
    %= \operatorname{Span} \{\phi_p : |p|=k\},
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
	\phi_p(x) 
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    %\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
 %The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
 It is known that 
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
%Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$. 
Therefore, for each $f\in L^2(\varphi)$, 
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
    \quad \text{in~} L^2(\varphi).
\end{equation}
%where $a_p=\langle f, \phi_p \rangle_{\varphi}$. 
Let
\begin{equation}\label{order}
    \kappa(f)
    %:=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.

In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
\begin{equation}
     \mathcal{P}
     %:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
     :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
%It is easy to see that $\mathcal{P} \subset L^2(\phi)$. 
It is easy to see that $\mathcal{P} \subset L^2(\varphi)$. 
%What's more, 
According to \cite[Fact 1.2]{MM},
for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
\begin{equation}\label{semigroupineq}
    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x).
\end{equation}
%That is to say the rate of decay of the semigroup depending on $\kappa(f)$. 
%The readers can find the prove in \cite[Fact 1.2]{MM}.

@@

Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{Li2011Measure} to \eqref{charequation}, we have that
\begin{equation}\label{chareq2}
        w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x)
\end{equation}

@@

For each $p\in \mathbb{Z}_+^d$, we define 
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
 We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa(g)b)t}\langle g, X_t\rangle \rightarrow\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0\leq\gamma<\beta$.

     Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{thm}
For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.  
 \begin{rem}
    If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle g, X_t\rangle \rightarrow \langle g, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0\leq\gamma<\beta$.

    Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure. 
 \end{rem}

\subsubsection{Critical Branching Rate}
For $g\in \mathcal{P}$, define 
$$\tilde{m}[g]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
{\color{red}where} 
$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g,\phi_p\rangle\phi_p(x).$$
See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
\begin{thm}\label{Theorem12}
Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle g,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by 
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
\end{thm}

@@

\begin{lem}\label{lemma24}
For any $0\leq \gamma < \beta$ there exists a constant $C>0$, we have the result:

@@

%new added
\section{Appendix}
